% David Mills - Cover Letter for City of Mt. Juliet
\documentclass[11pt,letterpaper]{letter}

\usepackage[empty]{fullpage}
\usepackage[hidelinks]{hyperref}
\usepackage{fontawesome5}
\usepackage{geometry}

\geometry{
  left=1in,
  right=1in,
  top=1in,
  bottom=1in
}

\signature{David Mills}
\address{
  \href{https://linkedin.com/in/davidsmillsjr}{\faIcon{linkedin} linkedin.com/in/davidsmillsjr} \\
  \href{https://github.com/visions85}{\faIcon{github} github.com/visions85} \\
  \href{https://github.com/visions85/homelab-infrastructure}{\faIcon{link} Portfolio: github.com/visions85/homelab-infrastructure}
}

\begin{document}

\begin{letter}{City of Mt. Juliet \\
Human Resources Department \\
Mt. Juliet, TN}

\opening{Dear Hiring Manager,}

I am writing to express my strong interest in the Information Technology Network/Systems Administrator II position with the City of Mt. Juliet. While I am transitioning from a different career path, my extensive hands-on experience designing, implementing, and maintaining production-grade infrastructure has equipped me with the technical expertise and problem-solving abilities essential for this role.

Over the past four years, I have built and maintained a multi-server infrastructure environment that directly aligns with the responsibilities outlined in your job description. My homelab isn't a casual hobby—it's been my intensive technical education and proving ground, where I've developed real-world skills in network administration, server management, cybersecurity, and infrastructure planning.

\textbf{My experience directly matches your key requirements:}

\textbf{Network \& Server Infrastructure:} I have architected and maintain 56+ containerized services across multiple servers, managing the full technology stack from network design through application deployment. I work extensively with virtualization, have implemented high-availability DNS infrastructure with BIND9 primary/secondary servers, and maintain comprehensive monitoring using Prometheus, Grafana, and InfluxDB—providing the visibility needed to ensure optimal network performance.

\textbf{Cybersecurity \& Best Practices:} I have implemented a multi-tier security architecture featuring CrowdSec IDS/IPS for threat detection and prevention, nginx reverse proxy with security hardening, and network segmentation across 8+ isolated Docker networks following zero-trust principles. I maintain SSL/TLS encryption across all services and have deployed SSO/OIDC using Authentik with PostgreSQL and Redis, integrating secure authentication across 20+ services.

\textbf{Disaster Recovery \& Documentation:} I maintain comprehensive technical documentation covering network architecture, service inventory, security configurations, and operational procedures. I implement automated backup strategies and version control all infrastructure configurations using Git, ensuring rapid recovery and change tracking.

\textbf{Windows \& Linux Administration:} While my homelab emphasizes Linux systems (SuSE, Red Hat, Arch, Debian), I have experience with Windows environments and am committed to rapidly expanding my Windows Server administration skills. I understand Active Directory concepts, PowerShell scripting, and have worked with cross-platform integration.

\textbf{Database Management:} I manage multiple PostgreSQL instances (versions 14-16), MariaDB 11.4, Redis caching layers, and InfluxDB for time-series data. I have experience with SQL queries, database optimization, and backup/recovery procedures.

\textbf{Problem-Solving \& Analysis:} I have developed strong troubleshooting skills working through complex multi-service issues spanning networking, storage, and application layers. Every challenge has taught me to methodically analyze problems, research solutions, and implement effective fixes—skills that translate directly to supporting city operations.

I understand that hiring someone transitioning careers involves consideration, but my hands-on experience demonstrates that I possess the technical foundation this position requires. I have dealt with the same challenges professional systems administrators face: service outages, performance optimization, security incidents, capacity planning, and infrastructure scaling. My GitHub portfolio provides detailed documentation of my infrastructure, demonstrating both technical capability and the clear documentation skills essential in municipal IT environments.

What I bring beyond technical skills is genuine enthusiasm for this work, proven ability to self-teach complex technologies, and strong commitment to public service. I'm eager to apply my expertise to support Mt. Juliet's city operations, public safety systems, and critical infrastructure while continuing to grow professionally in a team environment.

I would welcome the opportunity to discuss how my technical experience and dedication to continuous learning can benefit the City of Mt. Juliet. Thank you for considering my application.

\closing{Sincerely,}

\end{letter}

\end{document}
